SO2 Analysis

### 2015-08-25 pkg/gmrf/vignettesStuff/so2.rnw
should work with covariates having elements which aren't in the model
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1220 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<world,cache=TRUE,echo=FALSE,cache.extra=1>>=
worldShapeFile =  system(paste("find ", dataDir, 
				" -name *countries*.shp", sep=""),TRUE)
worldShapeFile = gsub("\\.shp$","",worldShapeFile)
world = readOGR(dataDir,gsub("[[:print::]+/","",worldShapeFile),
		stringsAsFactors=FALSE,verbose=FALSE)
@

>>>>

<<world,cache=TRUE,echo=FALSE,cache.extra=1>>=
worldShapeFile =  system(paste("find ", dataDir, 
				" -name *countries*.shp", sep=""),TRUE)[1]
worldShapeFile = gsub("\\.shp$","",worldShapeFile)
world = readOGR(dataDir,gsub("[[:print::]+/","",worldShapeFile),
		stringsAsFactors=FALSE,verbose=FALSE)
@
